A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Move to avoid forward reference

\paragraph{Outline} In Section~\ref{sect:review}, we review background on the
internal language of toposes, internal geometric theories and classifying
toposes. Section~\ref{sect:main} contains proofs of the main theorems in the
full generality of geometric theories. Restricting to Horn theories allows for
a treatment which is more algebraic and less logical in flavor. For the benefit
of readers with a more algebraic background, we include a mostly self-contained
account of the Horn case as Section~\ref{sect:horn}. We generalize our main
theorems to the higher-order case in Section~\ref{sect:higher-order} and
conclude with applications in Section~\ref{sect:applications}.

@@

@@

\subsection{Background on classifying toposes}
% XXX move up to avoid future reference

>>>>

\paragraph{Outline} In Section~\ref{sect:review}, we review background on the
internal language of toposes, classifying toposes and internal geometric theories.
Section~\ref{sect:main} contains proofs of the main theorems in the
full generality of geometric theories. Restricting to Horn theories allows for
a treatment which is more algebraic and less logical in flavor. For the benefit
of readers with a more algebraic background, we include a mostly self-contained
account of the Horn case as Section~\ref{sect:horn}. We generalize our main
theorems to the higher-order case in Section~\ref{sect:higher-order} and
conclude with applications in Section~\ref{sect:applications}.

@@

\subsection{Background on classifying toposes}
\label{sect:review-classifying-toposes}

@@
